---
title: "Visualization and Parspeech Sentiment using LIWC, FINN, Bing and NRC"
author: David Liao & Royce Carroll
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---


## I. Dataset Description
|        Countries        |     Object Names    |          Dict Type          |    Start-Date   |       Majority Parties        |       Minority Parties        |         
|-------------------------|:--------------------|-----------------------------|:---------------:|-------------------------------|-------------------------------|
| The UK House of Commons | hoc_MPs_Party_Year  | FINN, NRC, Bing, LIWC       |       1989    	| `Lab`,`Con`,`LibDem`          | `SDP`, `SNP`, `DUP`           |
| The Spanish Congresso   | cong_MPs_Party_Year | FINN, NRC, Bing, LIWC       |       1990      | `PP`,`PSOE`,`IU`              | `ERC`, `CiU`, `UPyD`          |
| The German Bundestag    | bt_MPs_Party_Year   | FINN, NRC, Bing, LIWC       |       1991      | `CDU/CSU`,`SPD`,`FDP`         | `GRUENE`, `independent`       |
| The Dutch Tweede Kamer  | tk_MPs_Party_Year   | FINN, NRC, Bing, LIWC       |       1995      | `VVD`,`PVV`, `CDA`            | `PVV`,`GL`, `D66`             |
| The Czech Poslanecká    | psp_MPs_Party_Year  | FINN, NRC, Bing             |       1993      | `??SSD`,`ODS`,`KS??M`           | `TOP 09 a Starostové`, `??SSD` |       
| The Finnish Eduskunta   | ed_MPs_Party_Year   | FINN, NRC, Bing             |       2009      | `SDP`,`Kok`, `Kesk`           | `RKP`, `KD`                   |      
| The Swedish Riksdagen   | rd_MPs_Party_Year   | FINN, NRC, Bing             |       1992      | `S`, `M`                      | `MP`, `L`, `KD`               |   

```{r I set up functions & purring the dataset, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
## Step1: installing multiple packages
sapply(c("ggpubr", "tidyverse", "readxl", "RColorBrewer", "parallel", "knitr", "DT"), require, character.only = TRUE)

# option = readline(prompt="opt for \"Set1\": ")  #  ColorBrewer suggestion : "Set1", "Set2", "Set3" , "BrBG", "Paired" 
option = "Set3" #  ColorBrewer suggestion : "Set1", "Set2", "Set3" , "BrBG", "Paired" 
options(scipen=999) 

## Step2: read dataset
setwd("~/Box/myBox/Speech Comparison/Sentiments")
bt_MPs <- read_csv("bt_MPs.csv")
cong_MPs <- read_csv("cong_MPs.csv")
ed_MPs <- read_csv("ed_MPs.csv")
hoc_MPs <- read_csv("hoc_MPs.csv")
psp_MPs <- read_csv("psp_MPs.csv")
rd_MPs <- read_csv("rd_MPs.csv")
tk_MPs <- read_csv("tk_MPs.csv")

## Step3: custom functions 
recodeData.by_party = function(i) { 
  # function recode for no liwc dictionary
  i %>% 
  filter(!party == "other") %>%
  mutate(Year = lubridate::year(date)) %>%
  group_by(party, Year) %>%
  summarise(Total_Sum = sum(terms),
            NegativeScores_party.FINN = sum(NegativeScores.FINN),
            PositiveScores_party.FINN = sum(PositiveScores.FINN),
            NegativeScores_party_mean.FINN = sum(NegativeScores.FINN)/Total_Sum,
            PositiveScores_party_mean.FINN = sum(PositiveScores.FINN)/Total_Sum,
            NegativeScores_party.Bing = sum(NegativeScores.Bing),
            PositiveScores_party.Bing = sum(PositiveScores.Bing),
            NegativeScores_party_mean.Bing = sum(NegativeScores.Bing)/Total_Sum,
            PositiveScores_party_mean.Bing = sum(PositiveScores.Bing)/Total_Sum,
            NegativeScores_party.Bing = sum(NegativeScores.Bing),
            PositiveScores_party.Bing = sum(PositiveScores.Bing),
            NegativeScores_party_mean.Bing = sum(NegativeScores.Bing)/Total_Sum,
            PositiveScores_party_mean.Bing = sum(PositiveScores.Bing)/Total_Sum,
            NegativeScores_party.NRC = sum(NegativeScores.NRC),
            PositiveScores_party.NRC = sum(PositiveScores.NRC),
            NegativeScores_party_mean.NRC = sum(NegativeScores.NRC)/Total_Sum,
            PositiveScores_party_mean.NRC = sum(PositiveScores.NRC)/Total_Sum) 
  }


recodeData.by_party.liwc = function(i) {
  # function recode for having liwc dictionary
  i %>% 
  filter(!party == "other") %>%
  mutate(Year = lubridate::year(date)) %>%
  group_by(party, Year) %>%
  summarise(Total_Sum = sum(terms),
            NegativeScores_party.FINN = sum(NegativeScores.FINN),
            PositiveScores_party.FINN = sum(PositiveScores.FINN),
            NegativeScores_party_mean.FINN = sum(NegativeScores.FINN)/Total_Sum,
            PositiveScores_party_mean.FINN = sum(PositiveScores.FINN)/Total_Sum,
            NegativeScores_party.Bing = sum(NegativeScores.Bing),
            PositiveScores_party.Bing = sum(PositiveScores.Bing),
            NegativeScores_party_mean.Bing = sum(NegativeScores.Bing)/Total_Sum,
            PositiveScores_party_mean.Bing = sum(PositiveScores.Bing)/Total_Sum,
            NegativeScores_party.Bing = sum(NegativeScores.Bing),
            PositiveScores_party.Bing = sum(PositiveScores.Bing),
            NegativeScores_party_mean.Bing = sum(NegativeScores.Bing)/Total_Sum,
            PositiveScores_party_mean.Bing = sum(PositiveScores.Bing)/Total_Sum,
            NegativeScores_party.NRC = sum(NegativeScores.NRC),
            PositiveScores_party.NRC = sum(PositiveScores.NRC),
            NegativeScores_party_mean.NRC = sum(NegativeScores.NRC)/Total_Sum,
            PositiveScores_party_mean.NRC = sum(PositiveScores.NRC)/Total_Sum,
            NegativeScores_party.LIWC = sum(negemo.LIWC),
            PositiveScores_party.LIWC = sum(posemo.LIWC),
            AffectScores.LIWC = sum(affect.LIWC),
            AnxScores.LIWC = sum(anx.LIWC),
            AngerScores.LIWC = sum(anger.LIWC),
            SadScores.LIWC = sum(sad.LIWC),
            NegativeScores_party_mean.LIWC = sum(negemo.LIWC)/Total_Sum,
            PositiveScores_party_mean.LIWC = sum(posemo.LIWC)/Total_Sum,
            AffectScores_party_mean.LIWC = sum(affect.LIWC)/Total_Sum,
            AnxScores_party_mean.LIWC = sum(anx.LIWC)/Total_Sum,
            AngerScores_party_mean.LIWC = sum(anger.LIWC)/Total_Sum,
            SadScores_party_mean.LIWC = sum(sad.LIWC)/Total_Sum) }
```

### The UK House of Commons 
```{r UK, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
hoc_MPs_Party_Year <- recodeData.by_party.liwc(hoc_MPs) %>% 
  filter(!Year == 1988 & !party == "other") %>%
  as.data.frame()

datatable(hoc_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```

### The Spanish Congresso
```{r Spane, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
cong_MPs_Party_Year <- recodeData.by_party.liwc(cong_MPs) %>% 
  filter(!Year == 1989 & !party == "other")

datatable(cong_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))

```

### The German Bundestag
```{r Germany, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
bt_MPs_Party_Year <- recodeData.by_party.liwc(bt_MPs) %>%
  as.data.frame()

datatable(bt_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```

### The Dutch Tweede Kamer
```{r Netherland, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
tk_MPs_Party_Year <- recodeData.by_party.liwc(tk_MPs) %>% 
  filter(!Year == 1994 & !party == "other")
datatable(tk_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```

### The Czech Poslaneck
```{r Czech, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
psp_MPs_Party_Year <- recodeData.by_party(psp_MPs) %>%  
  filter(!party == "other")
datatable(psp_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```

### The Finnish Eduskunta
```{r Finland, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ed_MPs_Party_Year <- recodeData.by_party(ed_MPs) %>% 
  filter(!party == "other")

datatable(ed_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```


### The Swedish Riksdagen
```{r Sweden, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
rd_MPs_Party_Year <- recodeData.by_party(rd_MPs) %>%  # Sweden
  filter(!party == "other")

datatable(rd_MPs_Party_Year, rownames = FALSE, filter="top",
          options = list(pageLength = 8, scrollX=T, initComplete = JS("function(settings, json) {","$('body').css({'font-family': 'Trebuchet MS'});","}")))
```


------

## II. The Number of Terms
```{r II set up functions & purring the dataset, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
## Step 1: Set up functions
linechart_fun.COUNT.FULL <- function(x, y) {
  # Exploring the number of terms in each speech by comparing full parties 
  ggplot(dat, aes(x = .data[[x]], y = .data[[y]]), group = party) +
    geom_line(aes(colour = party), size=2, show.legend = FALSE, alpha=0.7) + 
    geom_point(aes(shape = party), size=3, alpha =1) +
    scale_fill_manual(values = getPalette(length(summary(as.factor(unique(dat$party))))))+ #
    scale_shape_discrete(name = "Party", breaks = c(unique(dat$party))) +  
    scale_shape_manual(values = c(seq(1:length(summary(as.factor(unique(dat$party)))))))+
    scale_x_continuous(breaks = seq(0, max(dat$Year), 1))+
    theme_bw() +
    theme(legend.position = "bottom",   
          # here dealing with legend  // legend.position=c(.06, .3), legend.justification = c(0,0) 
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size=10)) +
    theme(plot.subtitle = element_text(size=10, color="black", family = "Trebuchet MS"),
          axis.text = element_text(size=5), axis.title=element_text(size = 10,face="bold"),
          axis.text.x = element_text(angle = 60, hjust = 1, size = 20 , family="Trebuchet MS"),
          axis.text.y = element_text(family = "Trebuchet MS", size = 10),
          plot.title =  element_text(family = "Trebuchet MS", size = 10),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "grey60", linetype = "blank"))+
    xlab(paste(str_sub(y, 1, 8), "Sentiment Scores", "/", str_replace(str_sub(y, -4),pattern = ".NRC", replacement = "NRC"))) +
    ylab(NULL) +
    labs(subtitle = "Unit: The Number of Terms")
  }


linechart_fun.COUNT.FULL.Facet <- function(x, y) {
  # Faceting the number of terms in each speech by comparing full parties 
  ggplot(dat, aes(x = .data[[x]], y = .data[[y]]), group = party) +
    geom_line(aes(colour = party), size = 1, show.legend = FALSE, alpha = 0.7) + 
    geom_point(aes(shape = party), size = 1.5, alpha = 1) +
    scale_fill_manual(values = getPalette(length(summary(as.factor(unique(dat$party))))))+ #
    scale_shape_discrete(name = "Party", breaks = c(unique(dat$party))) +  
    scale_shape_manual(values = c(seq(1:length(summary(as.factor(unique(dat$party)))))))+
    scale_x_continuous(breaks = seq(0, max(dat$Year), 1))+
    theme_bw() +
    theme(legend.position = "bottom",
          # here dealing with legend  // legend.position=c(.06, .3), legend.justification = c(0,0) 
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size=5))+
    theme(plot.subtitle = element_text(size = 5, family = "Trebuchet MS"),
          axis.text=element_text(size=5), 
          axis.title=element_text(size = 5, face="bold"), 
          strip.text = element_text(size= 5),
          axis.text.x = element_text(angle = 60, hjust = 1, size = 8, family="Trebuchet MS"),
          axis.text.y = element_text(family = "Trebuchet MS", size = 6),
          plot.title =  element_text(family = "Trebuchet MS", size = 4),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "grey60", linetype = "blank"))+
    xlab(paste(str_sub(y, 1, 8), "Sentiment Scores", "/", str_replace(str_sub(y, -4),pattern = ".NRC", replacement = "NRC"))) +
    ylab(NULL) +
    labs(subtitle = "Unit: The Number of Terms") +
    facet_wrap(~ party)
}

## Step 2: Purring the dataset
dat <- hoc_MPs_Party_Year #UK
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
hoc_MPs_Party_Year.COUNT <- map(names(hoc_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(hoc_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
hoc_MPs_Party_Year.COUNT.Facet <- map(names(hoc_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(hoc_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))

dat <- cong_MPs_Party_Year #Spain
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
cong_MPs_Party_Year.COUNT <-map(names(cong_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(cong_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
cong_MPs_Party_Year.COUNT.Facet <-map(names(cong_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(cong_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))

dat <- bt_MPs_Party_Year #Germany
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
bt_MPs_Party_Year.COUNT <-map(names(bt_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)], 
                              ~map(names(bt_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
bt_MPs_Party_Year.COUNT.Facet <-map(names(bt_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)], 
                              ~map(names(bt_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))

dat <- tk_MPs_Party_Year #Dutch 
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
tk_MPs_Party_Year.COUNT <-map(names(tk_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                              ~map(names(tk_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
tk_MPs_Party_Year.COUNT.Facet <-map(names(tk_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                              ~map(names(tk_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))

dat <- psp_MPs_Party_Year #Czech
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
psp_MPs_Party_Year.COUNT <-map(names(psp_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                               ~map(names(psp_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
psp_MPs_Party_Year.COUNT.Facet <-map(names(psp_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                               ~map(names(psp_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))


dat <- ed_MPs_Party_Year #Finland
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
ed_MPs_Party_Year.COUNT <-map(names(ed_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(ed_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
ed_MPs_Party_Year.COUNT.Facet <-map(names(ed_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(ed_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))

dat <- rd_MPs_Party_Year #Sweden
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
rd_MPs_Party_Year.COUNT <-map(names(rd_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(rd_MPs_Party_Year)[2], linechart_fun.COUNT.FULL, y = .x))
rd_MPs_Party_Year.COUNT.Facet <-map(names(rd_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(rd_MPs_Party_Year)[2], linechart_fun.COUNT.FULL.Facet, y = .x))
```


------

## 1. Full Parties
## 1.1.1 The UK House of Commons 
```{r II 1.1.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(hoc_MPs_Party_Year.COUNT[[i]][[1]])}
```

## 1.1.2 The UK House of Commons / Facet
```{r II 1.1.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(hoc_MPs_Party_Year.COUNT.Facet[[i]][[1]])}
```

## 1.2.1 The Spanish Congresso 
```{r II 1.2.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(cong_MPs_Party_Year.COUNT[[i]][[1]])
}
```
## 1.2.2 The Spanish Congresso / Facet
```{r II 1.2.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(cong_MPs_Party_Year.COUNT.Facet[[i]][[1]])
}
```

## 1.3.1 The German Bundestag
```{r II 1.3.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT[[i]][[1]])}
```
## 1.3.2 The German Bundestag / Facet
```{r II 1.3.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT.Facet[[i]][[1]])}
```

## 1.4.1 The Dutch Tweede Kamer 
```{r II 1.4.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(tk_MPs_Party_Year.COUNT[[i]][[1]])}
```
## 1.4.2 The Dutch Tweede Kamer / Facet
```{r II 1.4.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT.Facet[[i]][[1]])}
```

## 1.5.1 The Czech Poslanecká  
```{r II 1.5.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:6){
  print(psp_MPs_Party_Year.COUNT[[i]][[1]])}
```
## 1.5.2 The Czech Poslanecká / Facet
```{r II 1.5.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT.Facet[[i]][[1]])
}
```

## 1.6.1 The Finnish Eduskunta 
```{r II 1.6.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:6){
  print(ed_MPs_Party_Year.COUNT[[i]][[1]])}
```
## 1.6.2 The Finnish Eduskunta / Facet
```{r II 1.6.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT.Facet[[i]][[1]])}
```

## 1.7.1 The Swedish Riksdagen 
```{r II 1.7.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:6){
  print(rd_MPs_Party_Year.COUNT[[i]][[1]])}
```
## 1.7.2 The Swedish Riksdagen / Facet
```{r II 1.7.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
for (i in 1:12){
  print(bt_MPs_Party_Year.COUNT.Facet[[i]][[1]])}
```

------


## 2. Majority Parties

| Countries               |       Majority Parties        |      
|-------------------------|-------------------------------|
| The UK House of Commons | `Lab`,`Con`,`LibDem`          |
| The Spanish Congresso   | `PP`,`PSOE`,`IU`              |
| The German Bundestag    | `CDU/CSU`,`SPD`,`FDP`         | 
| The Dutch Tweede Kamer  | `VVD`,`PVV`, `CDA`            | 
| The Czech Poslanecká    | `??SSD`,`ODS`,`KS??M`           |  
| The Finnish Eduskunta   | `SDP`,`Kok`, `Kesk`           |     
| The Swedish Riksdagen   | `S`, `M`                      |    



```{r majority parties count recode, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Plot function 
linechart_fun.COUNT <- function(x, y) {
  # Exploring the number of terms in each speech by comparing full parties 
  ggplot(dat, aes(x = .data[[x]], y = .data[[y]]), group= party) +
    geom_line(aes(colour = party), size=1, show.legend = TRUE, alpha = 1) + 
    geom_point(aes(shape = party), size=1.5, alpha=0.7) +
    scale_x_continuous(breaks = seq(0, max(dat$Year), 1))+
    theme_bw() +
    theme(legend.position = "bottom",   
          # here dealing with legend  // legend.position=c(.06, .3), legend.justification = c(0,0) 
          legend.background = element_blank(),
          legend.key = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size=5)) +
    theme(plot.subtitle = element_text(size=5, color="black", family = "Trebuchet MS"),
          axis.text = element_text(size=5), axis.title=element_text(size = 5,face="bold"),
          axis.text.x = element_text(angle = 60, hjust = 1, size = 10 , family="Trebuchet MS"),
          axis.text.y = element_text(family = "Trebuchet MS", size = 5),
          plot.title =  element_text(family = "Trebuchet MS", size = 5),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "grey60", linetype = "blank")) +
    xlab(paste(str_sub(y, 1, 8), "Sentiment Scores", "/", str_replace(str_sub(y, -4),pattern = ".NRC", replacement = "NRC"))) +
    ylab(NULL) +
    labs(subtitle = "Unit: The Number of Terms")}



# Making a function for uniting the graphs  
ggarrage_show <- function(i){
  if (i %in% seq(1, 6, by=1)){
    # 1 Negative Scores / FINN 
    # 2 Negative Scores / Bing 
    # 3 Negative Scores / NRC
    # 4 Positive Scores / FINN 
    # 5 Positive Scores / Bing 
    # 6 Positive Scores / NRC
    ggarrange(hoc_MPs_Party_Year.COUNT[[i]][[1]], cong_MPs_Party_Year.COUNT[[i]][[1]], bt_MPs_Party_Year.COUNT[[i]][[1]], tk_MPs_Party_Year.COUNT[[i]][[1]],
              psp_MPs_Party_Year.COUNT[[i]][[1]], ed_MPs_Party_Year.COUNT[[i]][[1]], rd_MPs_Party_Year.COUNT[[i]][[1]],
              ncol = 4, nrow = 2, vjust = 4, hjust = -0.38,
              labels = c("UK House of Commons", "Spanish Congresso" , "German Bundestag ","Dutch Tweede Kamer","Czech Poslanecká", "Finnish Eduskunta", "Swedish Riksdagen"),
              common.legend = FALSE, font.label = list(size = 20, color = "black", face = "bold", family = "Trebuchet MS"),legend = "bottom")}
  else if (i %in% seq(7, 12, by=1)){ 
    # 7 LIWC Emotions Scores / Positve
    # 8 LIWC Emotions Scores / Negative
    # 9 LIWC Emotions Scores / Affect
    # 10 LIWC Emotions Scores / Anx
    # 11 LIWC Emotions Scores / Anger
    # 12 LIWC Emotions Scores / Sad        
    ggarrange(hoc_MPs_Party_Year.COUNT[[i]][[1]],cong_MPs_Party_Year.COUNT[[i]][[1]],bt_MPs_Party_Year.COUNT[[i]][[1]],tk_MPs_Party_Year.COUNT[[i]][[1]],
              ncol = 4, nrow = 2, vjust = 4, hjust = -0.38,
              labels = c("UK House of Commons", "Spanish Congresso" , "German Bundestag ","Dutch Tweede Kamer"),
              common.legend = FALSE, font.label = list(size = 20, color = "black", face = "bold", family = "Trebuchet MS"),legend = "bottom")} 
  else {print ("You should type the number between 1 to 12")}
}


# Purring majority party dataset
dat <- subset(hoc_MPs_Party_Year, party %in% c("Lab","Con","LibDem")) 
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
hoc_MPs_Party_Year.COUNT <- map(names(hoc_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(hoc_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))

dat <- subset(cong_MPs_Party_Year, party %in% c("PP","PSOE","IU")) 
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
cong_MPs_Party_Year.COUNT <-map(names(cong_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                                ~map(names(cong_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))


dat <- subset(bt_MPs_Party_Year, party %in% c("CDU/CSU","SPD","FDP")) 
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
bt_MPs_Party_Year.COUNT <-map(names(bt_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)], 
                              ~map(names(bt_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))


dat <- subset(tk_MPs_Party_Year, party %in% c("VVD","PVV", "CDA")) # just pick up three parties
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
tk_MPs_Party_Year.COUNT <-map(names(tk_MPs_Party_Year)[c(4,8,12, 5,9,13,16, 17, 18, 19, 20, 21)],
                              ~map(names(tk_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))


dat <- subset(psp_MPs_Party_Year, party %in% c("??SSD","ODS","KS??M")) # just pick up three parties
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
psp_MPs_Party_Year.COUNT <-map(names(psp_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                               ~map(names(psp_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))


dat <- subset(ed_MPs_Party_Year, party %in% c("SDP","Kok", "Kesk")) # just pick up three parties
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
ed_MPs_Party_Year.COUNT <-map(names(ed_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(ed_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))

dat <- subset(rd_MPs_Party_Year, party %in% c("S","M","C")) # just pick up three parties
colourCount <- length(summary(as.factor(unique(dat$party))))
getPalette <-  colorRampPalette(brewer.pal(colourCount, option))
rd_MPs_Party_Year.COUNT <-map(names(rd_MPs_Party_Year)[c(4,8,12, 5,9,13)],
                              ~map(names(rd_MPs_Party_Year)[2], linechart_fun.COUNT, y = .x))
```

## 2.1 The UK House of Commons 
## 2.1.1 Negative Scores / FINN 
```{r II 2.1.1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
ggarrage_show(1)
```


## 2.1.2 Negative Scores / Bing 

```{r II 2.1.2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
ggarrage_show(2)
```

## 2.1.3 Negative Scores / NRC

```{r II 2.1.3, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(3)
```

## 2.1.4 Positive Scores / FINN

```{r II 2.1.4, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(4)
```

## 2.1.5 Positive Scores / Bing

```{r II 2.1.5, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(5)
```

## 2.1.6 Positive Scores / NRC
```{r II 2.1.6, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(6)
```

## 2.1.7 LIWC Emotions Scores / Positve
```{r II 2.1.7, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(7)
```

## 2.1.8 LIWC Emotions Scores / Negative
```{r II 2.1.8, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(8)
```


## 2.1.9 LIWC Emotions Scores / Affect
```{r II 2.1.9, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(9)
```

## 2.1.10 LIWC Emotions Scores / Anx
```{r II 2.1.10, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(10)
```

## 2.1.11 LIWC Emotions Scores / Anger
```{r II 2.1.11, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(11)
```
    
## 2.1.12 LIWC Emotions Scores / Sad 
```{r II 2.1.12, fig.height=7, fig.width=15, message=FALSE, warning=FALSE}
ggarrage_show(12)
```



